Learning GENERAL Principles \\from Hundreds of Projects

### 2019-10-22 manuscript.tex
Updates from Overleaf

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
  emphstyle=\bfseries\color{black!80} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true]{{\small ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\begin{document}
\title{BUBBLE: Scaling Transfer Learning to 100s of Projects}

@@

% The paper headers
\markboth{IEEE Transactions on Software Engineering, submitted Oct `19}{Majumder \MakeLowercase{\textit{et al.}}: BUBBLE: Scaling Transfer Learning to 100s of Projects}

\IEEEtitleabstractindextext{%
\begin{abstract}
When one   exemplar project (the ``bellwether'') offers best advice, then it can be used to offer    advice for all other projects. These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).  Also, such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
for software quality issues).

But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
Hence,  we  BUBBLE, a bellwether based on
  hierarchical clustering. At each level, one bellwether is computed from sibling projects, then promoted up the tree.

   In studies of a corpus of   nearly 700 projects, we find that   the bellwether promoted to the top of the cluster tree is just as good as those found via a traditional bellwether analysis.    Further, this bellwether was 
found in    1.5 hours (versus 3 days needed for  prior work). 
  More importantly, BUBBLE   scales to larger problems since it uses a $O(m*(N/m)^2)$ analysis and not the $O(N^2)$ all pairs analysis used by standard bellwether methods.

 Accordingly, to   extract software quality rules from a   large corpus of SE, we recommend BUBBLE.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction,Scalable Method. 
\end{IEEEkeywords}}

@@

\section{Introduction}
How should we reason about SE quality?  Should we use  general models that hold over many projects? Or must we use an ever changing set of ideas that are   continually adapted to the task at hand? 
Or does the truth lie somewhere in-between?

This is an open and important question. After a decade of intensive research into automated software analytics, what general principles have we learned? While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).

Is that the best we can do? Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects? Not to mention, if software was ``patchwork'' of ideas,then that would  there would be no stable conclusions about what constitutes best practice for software engineering (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability would have detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.

One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis. A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}). Such small samples can never represent something as diverse as software engineering.

Reasoning across multiple projects is a complex task.
Krishna and Keung et al. reports some success in transferring conclusions from one project to another using ``bellwethers''\footnote{Traditionally,
the bellwether is the  leading sheep of a flock, with a bell on its neck.
In modern parlance, the bellwether is an 
  indicator or predictor of something.}
\bi
\item Find a  ``bellwether'' project that is exemplar for rest;
\item Draw conclusions from  that project.
\ei
This approach has successfully been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.

But Krishna and Keung et al.'s bellwether methods are very slow. When applied to the 679 projects studied here, it took 60 days to find and certify. There are many reasons for that including what how the models were certified (20 repeats  with different train/test sets)
and the complexity of the the analysis procedure (which including fixing class imbalance and feature selection). But the major cause of this slow down was that Krishna and Keung's   methods  required an $O(N^2)$ comparison between   $N=697$ projects.

\begin{figure}[!bh]
    \centering
    \includegraphics[width=\linewidth]{figs/predictive_power.png}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:predictive_power}
\end{figure}

This paper dramatically improves standard bellwether methods to find general conclusions from 697 projects.
 Our BUBBLE  methods applies divide and conquer  by utilizing a hierarchical clustering model to recursively divide the large number of projects in to smaller clusters. Starting at the leaves of that tree of clusters, BUBBLE finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree. The output of BUBBLE is the project promoted to the top of the tree of clusters.

 This paper evaluates the models generated from the bellwether project found by BUBBLE. In terms of the traditional measures such as recall, precision, Popt(20) or IFA, there is no significant performance different between BUBBLE's models and those found  via ``within'' learning (where quality models are learned just from data within a particular project) and ``all-pairs'' learning (where the bellwether is selected in the traditional way via a laborious $O(N^2)$ analysis).

In terms of {\em transfer} and {\em lessons learned},  this result has tremendous practical significance.  When new projects arrive, then even before there is much experience with those tasks,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),

While {\em many models} are generated via ``within'' learning, bellwethers only produce one model. And since the bellwether is equivalent to the other models,
 then when new projects appear, their quality cn be evalauted even before there is an extensive experience base with that particular project (just be applying the bellwether learend from r
 that means that general lessons about (a)~major quality issues;
 or (b)~best practices to avoid quality problems;
 or (c)~cost-benefit justifications for buying or building tools can be made stable across these 697 projects. Another advantage of the bellwethers

 Also, BUBBLE finds and certifies those general lessons much faster than traditional bellwether methods (30 hours vs 60 days).

 That is, lessons learned from BUBBLE's bellwether can be said to be general across multiple projects.

 The BUBBLE approach peformed better than ``within'' and similarly to ``all-pairs''. That is
 \bi
 \item
Learning from many other projects is bettter than learning just from your own project data;
\item
Taking the extra time required to learn via ``all-pairs'' is not necessary. This is important since BUBBLE runs mich faster than all-pairs (30 hours vs 60 days). 
\ei
More importantly, since it bases its conclusions from one exemplar bellwether project, BUBBLE can offer conclusions general to a very large set of projects. 
By reasoning over a tree of clusters with a branching factor of $b$, BUBBLE only requires $O(\log_bN)$  comparisons. This means BUBBLE will scale up better than traditional bellwether methods that need $O(N^2)$ comparisons. Here, we show results that are general to hundres of projects. In the future, our research goal is to find general conclusions across 10,000 projects, or perhaps even more.

The contributions of this paper are
\bi

\item \textbf{Showing inherent generality in SE} Since we show  offer a proof of generality in SE data sets via transfer learning. In this study we discover a source data set for transfer learner from a large number of potential projects, hence proving generality in the SE datasets where some dataset can act as examples for rest of them for defect prediction.

\item \textbf{An very fast algorithm to test generality in datasets:} A vary fast algorithm to test generality in other datasets with only minor changes.

\item \textbf{Hierarchical bellwethers as a transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm ``BUBBLE'' to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner. The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{BUBBLE}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.

\item \textbf{Rich Replication Package:} We have made available a rich replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} . The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.

\item \textbf{A new algorithm for transferring data from other projects, unlike prior works it can scale to large datasets:} Unlike previous studies for transfer learning, this method is order of magnitude faster for selecting a source project for transfer learning. Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between default bellwether and BUBBLE when running for 100 to 1,000,000 projects based on number of comparison required.

\item \textbf{Demo a fast bellwether method which run hours is comparable to a robust method which runs in months:}

@@

to the best of out knowledge bell/bubble is new high-water mark in qualitative empirical SE. XXX

This new transfer learning approach lets us ask and answer the following questions:

\begin{itemize}
        \item 
            \textbf{RQ1}:  Can we confirm bellwether on large datasets??

            \begin{RQ}{
                Default \textit{bellwether method} can find \textit{bellwether effect} in large datasets to discover source datasets for transfer learning. But this \textit{bellwether method} is very expensive making it infeasible for large datasets.}
            \end{RQ}

             \begin{RQ}{
                The proposed new \textit{transfer learner} ``BUBBLE'', using hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
            \end{RQ}
        \\   
        \\
        \\
        \\
        \\
        \\
        \item 
            \textbf{RQ3}:  Is faster bellwether effective?

            \begin{RQ}{
                The new transfer learner ``BUBBLE'' is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
            \end{RQ}

        \item 
            \textbf{RQ4}: Does learning from too many projects has detrimental effect?

            \begin{RQ}{
                Based on the results seen in this study we can see learning from too many projects do have detrimental effect in-term of predictive power and shows conclusion instability.}
            \end{RQ}

        \item 
            \textbf{RQ5}: What did we learn?

            \begin{RQ}{
                Based on the results seen in this study using Feature Subset Selector and Logistic Regression, the ``Bellwether Project'' learned only a 12\% of the features(mostly interface related metrics) are important for predicting defects.}
            \end{RQ}

    \end{itemize}

@@

\subsection{Motivation}
\label{sec:Motivation}
There are many reasons to seek stable general conclusions in software engineering. If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.

@@

\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable. Sawyer et al. agrees, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{figs/cost.png}
    \caption{Hypothetical cost comparison between BUBBLE and default Bellwether.}
    \label{fig:cost}
\end{figure}

Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.That is, they would predict that one model  will NOT  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply. Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model what works best.

The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering. Consider the hypothetical results of Figure~\ref{fig:predictive_power}. The \textcolor{ao(english)}{{\bf GREEN}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e. higher levels in the hierarchical cluster). After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1. In this case, while we could not offer a single model that cover {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters in that level. Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.

Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}. Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one. In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly change (whenever we jump from small community to small community); and (b)~the generality issues would be become open and urgent concerns for the SE analytics community.

\subsection{Related Work}
\label{sec:related}

In this section, we ask ``Why even bother to transfer lessons learned between projects?''. In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e. general models outperformed by specialized models localized to particular parts of the data. Menzies et al. showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective then rules learned from the global dataset. While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models. While local can cause conclusion instabilities, global models can miss details which is specific to certain dataset. So in this study, we review the evidence that if it is useful to explore more than just the local data. This evidence falls into four groups:

@@

\subsection{Metric Extraction}
\label{sec:Metric Extraction}

>>>>

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
  emphstyle=\bfseries\color{black!80} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true%
                ]{{\small  ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

@@

\begin{document}
\title{  Learning GENERAL Principles \\from Hundreds of     Projects}

@@

% The paper headers
\markboth{IEEE Transactions on Software Engineering, submitted Oct `19}{Majumder \MakeLowercase{\textit{et al.}}: GENERAL: Scaling Transfer Learning to 100s of Projects}

\IEEEtitleabstractindextext{%
\begin{abstract}

This paper seeks scalable methods for learning general lessons from hundreds of software projects.
When one   exemplar project (the ``bellwether'') offers the best advice, it can be used to offer    advice for
many others. These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).  Such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
for software quality issues).

But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
Hence,  we  propose GENERAL:  a novel bellwether based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For example, the defect prediction models found by GENERAL from
nearly 700 projects were  just as good as those found via  traditional methods.

@@

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction, Scalable Method. 
\end{IEEEkeywords}}

@@

\section{Introduction}

%   After a decade of intensive research into automated software analytics, what general principles have we learned? While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).

% Is that the best we can do?
How should we reason about software quality?  Should we use  general models that hold over many projects? Or must we use an ever-changing set of ideas that are   continually adapted to the task at hand? 
Or does the truth lie somewhere in-between?  
To say that another way:
\bi
\item
Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
\item
Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects?
\ei
If the latter were true then
 then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.

%One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis. A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}). Such small samples can never represent something as diverse as software engineering.

Finding general lessons across multiple projects is a complex task.
A new approach, that shows much promise,
is the ``bellwether'' method
 for   transferring conclusions between   projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}  (the bellwether is the  leading sheep of a flock, with a bell on its neck).  That method:
\bi
\item Finds a  ``bellwether'' project that is exemplar for the rest;
\item Draw conclusions from  that project.
\ei
This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.

In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
  tremendous practical significance.  When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),
 Further, since the bellwether is equivalent to the other models,
 then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (just by applying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

But existing  methods for bellwether transfer are very slow. When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers. There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection). But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.

This paper reports a novel approach  that dramatically improves on existing bellwether methods.
 Our GENERAL  method  uses hierarchical clustering model to recursively divide a large number of projects into smaller clusters. Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree. The output of GENERAL is the project promoted to the top of the tree of clusters.

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects is better than learning just from your own project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods.
For example:
\bi
\item
This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

\item 
 Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
 is inherently more scalable.
 \ei
\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figs/cost.png}
    \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
    \label{fig:cost}
\end{figure} 
Using GENERAL, we can  explore five research questions:

\begin{itemize}
        \item 
            \textbf{RQ1}:  What are the drawbacks of traditional bellwether  methods?

            \begin{RQ}{
                With hundreds of projects, traditional bellwether methods can discover  source datasets which offer general lessons for all the rest. But this traditional approach can require hundreds of hours of computations and will not scale to larger data sets.  }
            \end{RQ}

             \begin{RQ}{
                The proposed new  transfer learner called GENERAL uses hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
            \end{RQ}

        \item 
            \textbf{RQ3}:  Is this faster bellwether effective?

            \begin{RQ}{
                The new transfer learner GENERAL  is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
            \end{RQ}

        \item 
            \textbf{RQ4}: Does learning from too many projects have detrimental effect?

            \begin{RQ}{
                Based on the results seen in this study we can see learning from too many projects does have a detrimental effect in-term of predictive power and shows conclusion instability.}
            \end{RQ}

        \item 
            \textbf{RQ5}: What exactly did we learn from all those projects?

            \begin{RQ}{
                Based on the results seen in this study, our best models uses only a fraction of the features in the dataset. Looking at the selected metrics, we can conclude that in these 697 projects, code interface issues are the dominant factor on software defects. }
            \end{RQ}

    \end{itemize}
Overall, the  contributions of this paper are
\bi

\item \textbf{Hierarchical bellwethers for  transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm GENERAL to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner. The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{GENERAL}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.

\item \textbf{Showing inherent generality in SE}  In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).

\item \textbf{ Lessons   about software quality that are general
to hundreds of software projects:}
  As said above,    in  this sample of  697  projects,  we find that code  interface issues are the dominant factor on software defects.

\item \textbf{ Replication Package:} We have made available a  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} . The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.

@@

The rest of this paper is structured as follows. . Some background and related work are discussed in section~\ref{sec:literature}. Our algorithm GENERAL is described in section~\ref{GENERAL}. Data collection and experimental setup are in section~\ref{sec:Data Collection}. Followed by evaluation criteria in section~\ref{eval} and performance measures in section~\ref{sec:Measures}. The results and answers to the research questions are presented in section~\ref{sec:results}, which is followed by threats to validity in section~\ref{sec:validity}. Finally the conclusion is provided in section~\ref{sec:concl}.

@@

\subsection{Why Seek Generality?}
\label{sec:Motivation}
There are many reasons to seek stable general conclusions in software engineering. If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.

@@

\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable. Sawyer et al. agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.

@@

\begin{figure}[!b]
    \centering
    \includegraphics[width=\linewidth]{figs/predictive_power.png}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:predictive_power}
\end{figure}

\subsection{Why Shun Generality?}
Just to balance the above argument,
we add that   sometimes it is possible to learn from
{\em too much data}.
Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters. That is, they would predict that one model  will \underline{not}  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply. Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.

The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering. Consider the hypothetical results of Figure~\ref{fig:predictive_power}. The \textcolor{ao(english)}{{\bf GREEN}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e. higher levels in the hierarchical cluster). After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1. In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level. Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.

Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}. Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one. In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.

In summary, the above two sections lead to our  research question {\bf  RQ4}:
does learning from too many projects have detrimental effects. Later in this
paper, we will return to this issue.

\subsection{Why Transfer Knowledge?}
\label{sec:related}

In this section, we ask ``Why even bother to transfer lessons learned between projects?''. In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e. general models outperformed by specialized models localized to particular parts of the data. Menzies et al. showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective than rules learned from the global dataset. While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models. While local can cause conclusion instabilities, global models can miss details which are specific to a certain dataset. So in this study, we review the evidence that if it is useful to explore more than just the local data. This evidence falls into four groups:

@@
